The third interview transcript with Interviewer Santhosh Santhanam and Interviewee Saghana Mahesh Sarma

\begin{itemize}
    \item[] Santhosh Santhanam – Hi. I am working on an application for purchasing tickets online for the public transport system. Can you answer some questions for me?
    \item[] Saghana Mahesh Sarma – All right.
    \item[] Santhosh Santhanam – Can you tell me what is it that you do?
    \item[] Saghana Mahesh Sarma – I am a professor at McGill University. 
    \item[] Santhosh Santhanam – How often do you use public transport?
    \item[] Saghana Mahesh Sarma – I use it almost every day.
    \item[] Santhosh Santhanam – Have you encountered any issues while using the ticket vending machine?
    \item[] Saghana Mahesh Sarma – Once my receipt was not printed, I never faced any major issues.
    \item[] Santhosh Santhanam – Do you think the process of buying a ticket from the ticket vending machine is easy?
    \item[] Saghana Mahesh Sarma – Yes, it is easy to buy a ticket.
    \item[] Santhosh Santhanam –Would you use an online application to buy tickets or a monthly pass? 
    \item[] Saghana Mahesh Sarma – Yes, it would save a lot of time.
    \item[] Santhosh Santhanam – Do you prefer an email or paper receipt of your payment?
    \item[] Saghana Mahesh Sarma – I would prefer an email copy rather than keeping a paper copy safe.
    \item[] Santhosh Santhanam – How can we make the online application user-friendly?
    \item[] Saghana Mahesh Sarma – You could make it more user-friendly by having the option to select from multiple different languages.
    \item[] Santhosh Santhanam – Thank you for your suggestions. Have a good day!
\end{itemize}
\pagebreak