The second interview transcript with Interviewer Adwait Sambare and Interviewee Ganesh Viswanathan

\begin{itemize}
    \item[] Adwait Sambare – Hello. I am working on an application for a ticket vending machine. Would you mind answering a few questions? It will take only a few minutes.
    \item[] Ganesh Viswanathan – Okay sure!
    \item[] Adwait Sambare – What do you do in Montreal?
    \item[] Ganesh Viswanathan – I work at a Pharmaceutical Company in Montreal. 
    \item[] Adwait Sambare – Do you use the public transport system or use your own vehicle?
    \item[] Ganesh Viswanathan – I use both.
    \item[] Adwait Sambare – How often do you use the public transport system?
    \item[] Ganesh Viswanathan – I use it once or twice a week.
    \item[] Adwait Sambare – How is your experience with using ticket vending machines for buying tickets? 
    \item[] Ganesh Viswanathan – I think waiting in long queues is the biggest issue for me. That and an old-style display to buy tickets. It is a little confusing for someone using it for the first time.
    \item[] Adwait Sambare – Did you find instructions for payment easy?
    \item[] Ganesh Viswanathan – Not really, the screen to complete the payment using a card is small and dim.
    \item[] Adwait Sambare – Would you prefer buying tickets online from your mobile phone or your PC?
    \item[] Ganesh Viswanathan – Yes, I would, it will save a lot of time.
    \item[] Adwait Sambare – What kind of payment options would you like to use in the online application?
    \item[] Ganesh Viswanathan – I would like to use bank transfers and credit cards. 
    \item[] Adwait Sambare – What additional feature would you like to have in the application?
    \item[] Ganesh Viswanathan – I would like to have route planning and timings in the online application. 
    \item[] Adwait Sambare – Thank you so much for your time. Have a good day!
\end{itemize}
\pagebreak