The first interview transcript with Interviewer Sagar Sanghani and Interviewee Smit Parmar

\begin{itemize}
    \item[] Sagar Sanghani – Hi, Good Morning. I am working on a project regarding a ticket vending machine for public transportation. Can you spare a few minutes to answer a few questions regarding the same?
    \item[] Smit Parmar – Sure, Go ahead.
    \item[] Sagar Sanghani – Are you a student or a working professional?
    \item[] Smit Parmar – No, I am a student at Concordia University. 
    \item[] Sagar Sanghani – Do you use the public transport system?
    \item[] Smit Parmar – Yes, I use it every day for my commute to the university. I also use it to get around the city, it’s really efficient.
    \item[] Sagar Sanghani – So, tell me something you like and something you dislike about the ticket vending machine.
    \item[] Smit Parmar – I like the ticket vending machine because it is reliable. But I really dislike long queues to get a ticket or recharge my monthly pass.
    \item[] Sagar Sanghani – Okay. Was the ticket vending machine available in one of the languages that you were familiar with?
    \item[] Smit Parmar – Yes, it was available in English and French.
    \item[] Sagar Sanghani – Would you be interested in using an online application to purchase the ticket or buying a monthly pass?
    \item[] Smit Parmar – Yes, it would help.
    \item[] Sagar Sanghani – What additional features can you suggest for the application?
    \item[] Smit Parmar – I would like to have real-time updates on the location and timing of metro and buses
    \item[] Sagar Sanghani – What kind of payment options are you comfortable using online transactions?
    \item[] Smit Parmar – I can use a credit card and a debit card.
    \item[] Sagar Sanghani – Thank you so much for answering these questions. I appreciate your time. Have a good day!
\end{itemize}
\pagebreak

